|

### 2019-09-23 coverletter.Rmd
cover letter changed

We believe that it is an ideal fit for a short technical note in the Journal of Computational and Graphical Statistics. It describes a new graphical method that will be useful to people working in multivariate statistics.

>>>>

We believe that it is a good fit as a short technical note in the Journal of Computational and Graphical Statistics. Tew graphical method that will be useful to people working in multivariate analysis.
